---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**Note: this is a package made for a school assignment**

# LSfunctions

<!-- badges: start -->
<!-- badges: end -->

The goal of LSfunctions is to avoid repetitive work when working with Life Sciences data.

## Installation

You can install the development version of LSfunctions from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Justus789/LSfunctions")
```
## Usage

There are 4 functions in this package.
The first function is gram_change, which is used a conversion function. This function can change a unit into another unit. This way you dont have to calculate the conversion yourself.

The second function is dilute(), which can be used to calculate the last value if you have 3 values of the formula. The standard formula is C1 * V1 = C2 * V2.

The third function can help motivate you if you. With doorzetten() there are a few prepared answers to put in. In the ?doorzetten you can find a few of these answers.

The last function is files() which gives the working directory and a list of the directories from the given path. This can help when you are confused why a file cant be reached. Sometimes its because the file you are working at is further away from the working directory than you thought.

## Example

LSfunctions has multiple functions implemented.
For all of them an example will be shown.

```{r example}
library(LSfunctions)

#gram_change(1, "g", "mg")
#dilution(C1 = 20, V1 = 30, C2 = 10)
#doorzetten("bijna")
#files("kort")

```

In the ?desired_function() are more examples and tests if more information is needed. Especially for doorzetten() the Help page can be usefull to find the possible answers.




